A pipeline to analyse transcriptomic time-course data

### 2019-05-13 doc/manuscript/paper.tex
update text

While there are many methods that have been proposed for discrete aspects of time course data, the entire workflow for analysis of such data remains difficult, particularly for long, developmental time series. Most methods proposed for time course data are concerned with detecting genes that are changing over time (differential expression analysis), examples being \texttt{edge}\todo[Other methods to mention: impulse models, what else? Citations!]. However, with long time course datasets, particularly in developmental systems, a massive number of genes will show \emph{some} change. For example, in the \xxx system, over \xxx\% of genes are shown to be changing over time. The task in these settings is often not to detect changes in genes, but to categorize into biologically interpretable patterns the vast number of changes discovered.

@@

This workflow represents an integration of both novel implementations of previously established methods and new methodologies for the settings of developmental time series. We provide the various steps of the workflow as functions in a R package, \citettt{\xxx}, along with command-line tools for running the entire workflow in a single command.

@@

Several techniques for mRNA-expression analysis were

>>>>

While there are many methods that have been proposed for discrete components of time course data, the entire workflow for analysis of such data remains difficult, particularly for long, developmental time series. Most methods proposed for time course data are concerned with detecting genes that are changing over time (differential expression analysis), examples being \texttt{edge}\todo[Other methods to mention: impulse models, what else? Citations!]. However, with long time course datasets, particularly in developmental systems, a massive number of genes will show \emph{some} change. For example, in the \xxx system, over \xxx\% of genes are shown to be changing over time. The task in these settings is often not to detect changes in genes, but to categorize into biologically interpretable patterns the vast number of changes discovered. In this context, the clustering of genes and interpretation of the genes can be far more relevant, and the

@@

This workflow represents an integration of both novel implementations of previously established methods and new methodologies for the settings of developmental time series. We provide the various steps of the workflow as functions in a R package, \citettt{\xxx}, along with command-line tools for running the entire workflow.

@@

A vast number of techniques Several techniques for mRNA-expression analysis
